DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2017-01-26 2015CompleteDerivation/completeDerivation.tex
Minor fixes

	As a final note: we caution against automatically thinking that the classical assumption is valid for all macroscopic systems. It is conceptually possible to have a macroscopic system where a clear independent state cannot be assigned to each part, in which case the assumption would not hold.\footnote{This is the case in Bose-Einstein condensates \cite{BEC}, where each part becomes indistinguishable from the rest.}
\end{rationale}

@@

\bibitem{BEC} Pitaevskii, L. P., Stringari, S.: Bose–Einstein Condensation. Clarendon Press, Oxford (2003)

>>>>

	As a final note: we caution against automatically thinking that the classical assumption is valid for all macroscopic systems. It is conceptually possible to have a macroscopic system where a clear independent state cannot be assigned to each part, in which case the assumption would not hold.\footnote{For example, this is the case in Bose-Einstein condensates \cite{BEC}.}
\end{rationale}

@@

\bibitem{BEC} Pitaevskii, L. P., Stringari, S.: Bose–-Einstein Condensation. Clarendon Press, Oxford (2003)
